---
title: "01_code-results-discussion"
author: "Asilata"
date: "May 2021"
output:
  prettydoc::html_pretty:
    theme: architect
    highlight: github
---

This is a practice project on text analysis using `stm`. I'll be analysing J. P. Narayan's 1959 text, "A Plea for the Reconstruction of the Indian Polity".

The source is an extract published on [Seminar](https://www.india-seminar.com) in 2001 which can be accessed [here](https://www.india-seminar.com/2001/506/506%20extract.html).

Since it is an essay, I've "chunked" it into paragraphs through a complicated process involving **Word** for removing commas, colons, semi-colons, quotes, etc. Then I added double quotes to create paragraphs, copy-pasted the whole thing into **Notepad**, and then copy-pasted it again into a column in the recon.csv file. **Must find a better way to do it!**

## Get started

```{r setup, include=FALSE}
rm(list=ls(all.names=TRUE))
knitr::opts_chunk$set(eval=FALSE)
```

### Load Packages

```{r load packages}
library(stm)
```

### Load Data

```{r load data}
recon <- read.csv("data/recon.csv")
names(recon)
```

## Preprocess data

```{r preprocess}
# Pre-process

temp <- textProcessor(documents = recon$text, metadata = recon)
meta <- temp$meta
vocab <- temp$vocab
docs <- temp$documents

# prep documents in correct format
out <- prepDocuments(docs, vocab, meta)
docs <- out$documents
vocab <- out$vocab
meta <- out$meta
```

## Run a model

We're excluding the `max.em.its = 15` argument from the end of the line of code (which keeps the iterations to a certain number, in this case, 15) to let the model reach convergence.

```{r model}
model <- stm(docs, vocab, 15, prevalence = ~ text, data = meta, seed = 15)
```

## Find Top Words using model

```{r top words}
# Top Words
labelTopics(model)

# Example Docs
findThoughts(model, texts = meta$text, n=2,topics = 1:15)
```

## Analyse Topics

**This is incomplete. Refer to Rochelle's code: 08-4_STM.Rmd**

```{r analyse topics}
# Corpus Summary
plot.STM(model)

# Estimate Covariate Effects
prep <- estimateEffect(1:15 ~ text, model, meta = meta, documents=docs)

```
